\section
{Publications}
{Publications}
{PDF:Publications}

\subsection
{Editorial Material}
{Editorial Material}
{PDF:Editorial_Material}

\GapNoBreak
\NumberedItem{\makebox[0.8cm][r]{[11]}}
\href{False}
{Measuring Impact}
\newline
{\textbf{Amaral LAN}}
\newline
\textit{The Scientist}
39186 (2014).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[10]}}
\href{/people/amaral/envisioning-sophisticated-electronic-health-records-through-lens-health-care-reform}
{Envisioning sophisticated electronic health records through the lens of health care reform}
\newline
Weiss CH, {\textbf{Amaral LAN}}
\newline
\textit{Am. J. of Respirat. and Crit. Care Med.}
    188:
636--638 (2013).
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[9]}}
\href{False}
{Moving the science of quality improvement in critical care medicine forward}
\newline
Weiss CH, {\textbf{Amaral LAN}}
\newline
\textit{Am. J. of Respirat. and Crit. Care Med.}
    182:
1461--1462  (2010).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[8]}}
\href{/people/amaral/complex-systems-view-educational-policy-research}
{Complex systems view of educational policy research}
\newline
Maroulis S, Guimer\`a R, Petry H, Stringer MJ, Gomez LM, {\textbf{Amaral LAN}}, Wilensky U
\newline
\textit{Science}
    330:
38--39 (2010).
    [{\em{Citations:}}  25 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[7]}}
\href{/people/amaral/a-truer-measure-of-our-ignorance}
{A truer measure of our ignorance}
\newline
{\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    105:
6795--6796 (2008).
    [{\em{Citations:}}  15 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[6]}}
\href{/people/amaral/ecological-engineering-and-sustainabitity-a-new-opportunity-for-chemical-engineering}
{Ecological Engineering and Sustainabitity: A New Opportunity for Chemical Engineering}
\newline
Stouffer DB, Ng CA, {\textbf{Amaral LAN}}
\newline
\textit{AICHE Journal}
    54:
3040--3047 (2008).
    [Featured on cover]
    [{\em{Citations:}}  5 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[5]}}
\href{/people/amaral/complex-systems-a-new-paradigm-for-the-integrative-study-of-management-physical-and-technological-systems}
{Complex systems - A new paradigm for the integrative study of management, physical, and technological systems}
\newline
{\textbf{Amaral LAN}}, Uzzi B
\newline
\textit{Management Science}
    53:
1033--1035 (2007).
    [{\em{Citations:}}  46 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[4]}}
\href{/people/amaral/lies-damned-lies-and-statistics}
{Lies, damned lies and statistics}
\newline
{\textbf{Amaral LAN}}, Guimer\`a R
\newline
\textit{Nature Physics}
    2:
75--76 (2006).
    [{\em{Citations:}}  14 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[3]}}
\href{/people/amaral/novel-collaborations-within-experienced-teams-lead-to-best-research-outcomes}
{Novel collaborations within experienced teams lead to best research outcomes}
\newline
{\textbf{Amaral LAN}}
\newline
\textit{Annals of Vascular Surgery}
    19:
753-754 (2005).
    [Featured on cover]
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[2]}}
\href{False}
{Virtual Round Table on ten leading questions for network research}
\newline
{\textbf{Amaral LAN}}, Barrat A, Barabasi AL, Caldarelli G, De los Rios P, Erzan A, Kahng B, Mantegna R, Mendes JFF, Pastor-Satorras R, Vespignani A 
\newline
\textit{European Physical Journal B}
    38:
143--145  (2004).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[1]}}
\href{/people/amaral/complex-systems-and-networks-challenges-and-opportunities-for-chemical-and-biological-engineers}
{Complex systems and networks: challenges and opportunities for chemical and biological engineers}
\newline
{\textbf{Amaral LAN}}, Ottino JM
\newline
\textit{Chemical Engineering and Science}
    59:
1653--1666 (2004).
    [{\em{Citations:}}  33 (Scopus) ]
\newline
\Gap
~
\Gap

\vspace*{0.2cm}\subsection
{Review Articles}
{Review Articles}
{PDF:Review_Articles}

\GapNoBreak
\NumberedItem{\makebox[0.8cm][r]{[6]}}
\href{/people/amaral/complex-networks-augmenting-the-framework-for-the-study-of-complex-systems}
{Complex networks - Augmenting the framework for the study of complex systems}
\newline
{\textbf{Amaral LAN}}, Ottino JM
\newline
\textit{European Physical Journal B}
    38:
147--162 (2004).
    [{\em{Citations:}}  205 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[5]}}
\href{/people/amaral/sexual-networks-implications-for-the-transmission-of-sexually-transmitted-infections}
{Sexual networks: implications for the transmission of sexually transmitted infections}
\newline
Liljeros F, Edling CR, {\textbf{Amaral LAN}}
\newline
\textit{Microbes and Infections}
    5:
189--196 (2003).
    [{\em{Citations:}}  133 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[4]}}
\href{/people/amaral/fractal-dynamics-in-physiology-alterations-with-disease-and-aging}
{Fractal dynamics in physiology: Alterations with disease and aging}
\newline
Goldberger AL, {\textbf{Amaral LAN}}, Hausdorff JM, Ivanov PC, Peng CK, Stanley HE
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    99:
2466--2472 (2002).
    [Featured on cover]
    [{\em{Citations:}}  824 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[3]}}
\href{/people/amaral/self-organized-complexity-in-economics-and-finance}
{Self-organized complexity in economics and finance}
\newline
Stanley HE, {\textbf{Amaral LAN}}, Buldyrev SV, Gopikrishnan P, Plerou V, Salinger MA
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    99:
2561--2565 (2002).
    [{\em{Citations:}}  39 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[2]}}
\href{/people/amaral/from-1f-noise-to-multifractal-cascades-in-heartbeat-dynamics}
{From 1/f noise to multifractal cascades in heartbeat dynamics}
\newline
Ivanov PC, {\textbf{Amaral LAN}}, Goldberger AL, Havlin S, Rosenblum MG, Stanley HE, Struzik ZR
\newline
\textit{Chaos}
    11:
641--652 (2001).
    [{\em{Citations:}}  190 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[1]}}
\href{False}
{Multifractalidade do ritmo cardiaco}
\newline
{\textbf{Amaral LAN}}, Ivanov PC, Goldberger AL, Havlin S, Stanley HE 
\newline
\textit{Gazeta de Fisica }
    22:
4--8  (1999).
    [Featured on cover]
\newline
\Gap
~
\Gap

\vspace*{0.2cm}\subsection
{Research Articles}
{Research Articles}
{PDF:Research_Articles}

\GapNoBreak
\NumberedItem{\makebox[0.8cm][r]{[119]}}
\href{/people/amaral/depletion-shine-dalgarno-sequences-within-bacterial-coding-regions-expression-dependent}
{Depletion of Shine-Dalgarno sequences within bacterial coding regions Is expression dependent}
\newline
Yang C, Hockenberry AJ, Jewett MC, {\textbf{Amaral LAN}}
\newline
\textit{G3 : Genes | Genomes | Genetics}
    6:
3467--3474 (2016).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[118]}}
\href{/people/amaral/network-approach-discerning-identities-c-elegans-free-moving-population}
{A network approach to discerning the identities of C. elegans in a free moving population}
\newline
Winter PB, Brielmann RB, Timkovich NP, Navarro HT, Teixeira-Castro A, Morimoto RI, {\textbf{Amaral LAN}}
\newline
\textit{Scientific Reports}
    6:
34859 (2016).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[117]}}
\href{/people/amaral/differences-collaboration-patterns-across-discipline-career-stage-and-gender}
{Differences in collaboration patterns across discipline, career stage, and gender}
\newline
Zeng XHT, Duch J, Sales-Pardo M, Moreira JAG, Radicchi F, Ribeiro HV, Woodruff TK, {\textbf{Amaral LAN}}
\newline
\textit{PLOS Biology}
    14:
1002573 (2016).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[116]}}
\href{/people/amaral/nullseq-tool-generating-random-coding-sequences-desired-amino-acid-and-gc-contents}
{NullSeq: A tool for generating random coding sequences with desired amino acid and GC contents}
\newline
Liu SS, Hockenberry AJ, Lancichinetti A, Jewett MC, {\textbf{Amaral LAN}}
\newline
\textit{PLOS Computational Biology}
    12:
1005184 (2016).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[115]}}
\href{/people/amaral/cross-evaluation-metrics-estimate-significance-creative-works}
{Cross-evaluation of metrics to estimate the significance of creative works}
\newline
Wasserman M, Zeng XHT, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    112:
1281--1286 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[114]}}
\href{/people/amaral/social-embeddedness-online-weight-management-programme-linked-greater-weight-loss}
{Social embeddedness in an online weight management programme is linked to greater weight loss}
\newline
Poncela-Casasnovas J, Spring B, McClary D, Moller AC, Mukogo R, Pellegrini CA, Coons MJ, Davidson M, Mukherjee S, {\textbf{Amaral LAN}}
\newline
\textit{Journal of the Royal Society Interface}
    12:
20140686 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[113]}}
\href{/people/amaral/high-reproducibility-and-high-accuracy-method-automated-topic-classification}
{High-reproducibility and high-accuracy method for automated topic classification}
\newline
Lancichinetti A, Sirer MI, Wang JX, Acuna D, Kording K, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review X}
    5:
011007 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[112]}}
\href{/people/amaral/currents-beneath-rising-tide-school-choice-analysis-student-enrollment-flows-chicago-public-schools}
{The currents beneath the rising tide of school choice: An analysis of student enrollment flows in the Chicago Public Schools}
\newline
Sirer MI, Maroulis S, Guimer\`a R, Wilensky U, {\textbf{Amaral LAN}}
\newline
\textit{Journal of Policy Analysis and Management,}
    34:
358--377 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[111]}}
\href{/people/amaral/correlations-between-user-voting-data-budget-and-box-office-films-internet-movie-database}
{Correlations between user voting data, budget, and box office for films in the Internet Movie Database}
\newline
Wasserman M, Mukherjee S, Scott K, Zeng XHT, Radicchi F, {\textbf{Amaral LAN}}
\newline
\textit{Journal of the Association for Information Science and Technology}
    66:
858--868 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[110]}}
\href{/people/amaral/scaling-and-optimal-synergy-two-principles-determining-microbial-growth-complex-media}
{Scaling and optimal synergy: Two principles determining microbial growth in complex media}
\newline
Massucci FA, Guimer\`a R, {\textbf{Amaral LAN}}, Sales-Pardo M
\newline
\textit{Physical Review E}
    91:
062703 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[109]}}
\href{/people/amaral/distribution-asymptotic-number-citations-sets-publications-researcher-or-academic-department-are-consistent-discrete-lognormal-model}
{The distribution of the asymptotic number of citations to sets of  publications by a researcher or from an academic department are consistent with a discrete lognormal model}
\newline
Moreira JAG, Zeng XHT, {\textbf{Amaral LAN}}
\newline
\textit{PLoS ONE}
    10:
e0143108 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[108]}}
\href{/people/amaral/dynamics-and-heterogeneity-fate-determinant-during-transition-towards-cell-differentiation}
{Dynamics and heterogeneity of a fate determinant during transition towards cell differentiation}
\newline
Pelaez N, Gavalda-Miralles A, Wang B, Tejedor Navarro H, Gudjonson H, Rebay I, Dinner AR, Katsaggelos AK, {\textbf{Amaral LAN}}, Carthew RW
\newline
\textit{eLife}
    4:
e08924 (2015).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[107]}}
\href{/people/amaral/impact-heterogeneity-and-socioeconomic-factors-individual-behavior-decentralized-sharing-ecosystems}
{Impact of heterogeneity and socioeconomic factors on individual behavior in decentralized sharing ecosystems}
\newline
Gavald\`a-Miralles A, Choffnes DR, Otto JS, Sanchez MA, Bustamante FE, {\textbf{Amaral LAN}}, Duch J, Guimer\`a R
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    111:
15322--15327 (2014).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[106]}}
\href{/people/amaral/user-behavior-and-change-file-sharers-and-copyright-laws}
{User Behavior and Change: File-sharers and Copyright Laws}
\newline
Gavald\`a-Miralles A, Otto JS, Bustamante FE, {\textbf{Amaral LAN}}, Duch J, Guimer\`a R
\newline
\textit{Proceedings of the 10th ACM CoNEXT 2014}
319--324 (2014).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[105]}}
\href{/people/amaral/quantifying-position-dependent-codon-usage-bias}
{Quantifying position-dependent codon usage bias}
\newline
Hockenberry AJ, Sirer MI, {\textbf{Amaral LAN}}, Jewett MC
\newline
\textit{Molecular Biology and Evolution}
    31:
1880--1893 (2014).
    [{\em{Citations:}}  2 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[104]}}
\href{/people/amaral/adoption-high-impact-innovation-homogeneous-population}
{Adoption of a high-impact innovation in a homogeneous population}
\newline
Weiss CH, Poncela-Casasnovas J, Glaser JI, Pah AR, Persell SD, Baker DW, Wunderink RG, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review X}
    4:
041008 (2014).
    [{\em{Citations:}}  2 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[103]}}
\href{/people/amaral/solution_to_challenge}
{A solution to the challenge of optimization on golf-course-like fitness landscapes}
\newline
Melo HPM, Franks A, Moreira AA, Diermeier D, Andrade Jr JS, {\textbf{Amaral LAN}}
\newline
\textit{PLOS ONE}
    8:
e78401 (2013).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[102]}}
\href{/people/amaral/move-move-dynamics-advantage-chess-matches-reveals-population-level-learning-game}
{Move-by-move dynamics of the advantage in chess matches reveals population-level learning of the game}
\newline
Ribeiro HV, Mendes RS, Lenzi EK, del Castillo-Mussot M, {\textbf{Amaral LAN}}
\newline
\textit{PLOS ONE}
    8:
e54165 (2013).
    [{\em{Citations:}}  4 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[101]}}
\href{/people/amaral/changes-task-related-functional-connectivity-across-multiple-spatial-scales-are-related-reading-performance}
{Changes in task-related functional connectivity across multiple spatial scales are related to reading performance}
\newline
Wang JX, Bartolotti J, {\textbf{Amaral LAN}}, Booth JR
\newline
\textit{PLOS ONE}
    8:
e59204 (2013).
    [{\em{Citations:}}  4 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[100]}}
\href{/people/amaral/use-global-metabolic-network-predict-organismal-metabolic-networks}
{Use of a global metabolic network to predict organismal metabolic networks}
\newline
Pah AR, Guimer\`a R, Mustoe AM, {\textbf{Amaral LAN}}
\newline
\textit{Scientific Reports}
    3:
1695 (2013).
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[99]}}
\href{/people/amaral/impact-individual-biases-consensus-formation}
{The impact of individual biases on consensus formation}
\newline
Sales-Pardo M, Diermeier D, {\textbf{Amaral LAN}}
\newline
\textit{PLOS ONE}
    8:
e58989 (2013).
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[98]}}
\href{/people/amaral/possible-role-resource-requirements-and-academic-career-choice-risk-gender-differences-publication-rate-and-impact}
{The possible role of resource requirements and academic career-choice risk on gender differences in publication rate and impact}
\newline
Duch J, Zeng XHT, Sales-Pardo M, Radicchi F, Otis S, Woodruff TK, {\textbf{Amaral LAN}}
\newline
\textit{PLOS ONE}
    7:
e51332 (2012).
    [{\em{Citations:}}  20 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[97]}}
\href{/people/amaral/rationality-irrationality-and-escalating-behavior-lowest-unique-bid-auctions}
{Rationality, irrationality and escalating behavior in lowest unique bid auctions}
\newline
Radicchi F, Baronchelli A, {\textbf{Amaral LAN}}
\newline
\textit{PLoS ONE}
    7:
e29910 (2012).
    [{\em{Citations:}}  13 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[96]}}
\href{/people/amaral/macro-level-modeling-response-_c-elegans_-reproduction-chronic-heat-stress}
{Macro-level modeling of the response of C. elegans reproduction to chronic heat stress}
\newline
McMullen PD, Aprison EZ, Winter PB, {\textbf{Amaral LAN}}, Morimoto RI, Ruvinsky I
\newline
\textit{PLoS Computational Biology}
    8:
e1002338 (2012).
    [{\em{Citations:}}  9 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[95]}}
\href{/people/amaral/phenomenological-model-predicting-catabolic-potential-arbitrary-nutrient}
{Phenomenological model for predicting the catabolic potential of an arbitrary nutrient}
\newline
Seaver SMD, Sales-Pardo M, Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{PLOS Computational Biology}
    8:
e1002762 (2012).
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[94]}}
\href{/people/amaral/prompting-physicians-address-daily-checklist-and-process-care-and-clinical-outcomes-single-site-study}
{Prompting physicians to address a daily checklist and process of care and clinical outcomes: A single-site study}
\newline
Weiss CH, Moazed F, McEvoy CA, Singer BD, Szleifer I, {\textbf{Amaral LAN}}, Kwasny M, Watts CM, Persell SD, Baker DW, Sznajder JI, Wunderink RG
\newline
\textit{American Journal of Respiratory and Critical Care Medicine}
    184:
680--686 (2011).
    [{\em{Citations:}}  58 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[93]}}
\href{/people/amaral/duality-between-time-series-and-networks}
{Duality between time series and networks}
\newline
Campanharo ASLO, Sirer MI, Malmgren RD, Ramos FM, {\textbf{Amaral LAN}}
\newline
\textit{PLoS ONE}
    6:
e23378 (2011).
    [{\em{Citations:}}  36 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[92]}}
\href{/people/amaral/role-body-mass-diet-contiguity-and-food-web-structure}
{The role of body mass in diet contiguity and food-web structure}
\newline
Stouffer DB, Rezende EL, {\textbf{Amaral LAN}}
\newline
\textit{Journal of  Animal Ecology}
    80:
632--639 (2011).
    [{\em{Citations:}}  21 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[91]}}
\href{/people/amaral/strange-bedfellows-community-identification-bittorrent}
{Strange bedfellows: Community identification in BitTorrent}
\newline
Choffnes D, Duch J, Malmgren RD, Guimera R, Bustamante F, {\textbf{Amaral LAN}}
\newline
\textit{Proceedings of the 9th ACM IPTPS International Conference on Peer-to-Peer Systems}
13 (2010).
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[90]}}
\href{/people/amaral/quantifying-performance-individual-players-team-activity}
{Quantifying the performance of individual players in a team activity}
\newline
Duch J, Waitzman JS, {\textbf{Amaral LAN}}
\newline
\textit{PLoS ONE}
    5:
e10937 (2010).
    [{\em{Citations:}}  46 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[89]}}
\href{/people/amaral/origin-compartmentalization-food-webs}
{Origin of compartmentalization in food webs}
\newline
Guimer\`a R, Stouffer DB, Sales-Pardo M, Leicht EA, Newman MEJ, {\textbf{Amaral LAN}}
\newline
\textit{Ecology}
    91:
2941--2951 (2010).
    [{\em{Citations:}}  43 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[88]}}
\href{/people/amaral/statistical-validation-global-model-distribution-ultimate-number-citations-accrued-papers-published-scientific-journal}
{Statistical validation of a global model for the distribution of the ultimate number of citations accrued by papers published in a scientific journal}
\newline
Stringer MJ, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{Journal of the American Society for Information Science and Technology}
    61:
1377--1385 (2010).
    [{\em{Citations:}}  31 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[87]}}
\href{/people/amaral/role-mentorship-protege-performance}
{The role of mentorship in protege performance}
\newline
Malmgren RD, Ottino JM, {\textbf{Amaral LAN}}
\newline
\textit{Nature}
    463:
622--626 (2010).
    [{\em{Citations:}}  22 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[86]}}
\href{/people/amaral/physically-grounded-approach-estimating-gene-expression-microarray-data}
{Physically grounded approach for estimating gene expression from microarray data}
\newline
McMullen PD, Morimoto RI, Amaral, LAN
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    107:
13690--13695 (2010).
    [{\em{Citations:}}  6 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[85]}}
\href{/people/amaral/universality-human-correspondence-activity}
{On Universality in Human Correspondence Activity}
\newline
Malmgren RD, Stouffer DB, Campanharo ASLO, {\textbf{Amaral LAN}}
\newline
\textit{Science}
    325:
1696--1700 (2009).
    [{\em{Citations:}}  92 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[84]}}
\href{/people/amaral/levels-of-complexity-in-scale-invariant-neural-signals}
{Levels of complexity in scale-invariant neural signals}
\newline
Ivanov PC, Ma QDY, Bartsch RP, Hausdorff JM, {\textbf{Amaral LAN}}, Schulte-Frohlinde V, Stanley HE, Yoneyama M
\newline
\textit{Physical Review E}
    79:
041920 (2009).
    [{\em{Citations:}}  34 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[83]}}
\href{/people/amaral/detection-of-node-group-membership-in-networks-with-group-overlap}
{Detection of node group membership in networks with group overlap}
\newline
Sawardecker EN, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{European Physical Journal B}
    67:
277--284 (2009).
    [Featured on cover]
    [{\em{Citations:}}  25 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[82]}}
\href{/people/amaral/characterizing-individual-communication-patterns}
{Characterizing individual communication patterns}
\newline
Malmgren RD, Hofman JM, {\textbf{Amaral LAN}}, Watts DJ
\newline
\textit{Proceedings of the 15th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}
609-615 (2009).
    [{\em{Citations:}}  22 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[81]}}
\href{/people/amaral/price-dynamics-in-political-prediction-markets}
{Price dynamics in political prediction markets}
\newline
Majumder SR, Diermeier D, Rietz TA, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    106:
679--684 (2009).
    [{\em{Citations:}}  8 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[80]}}
\href{/people/amaral/comparison-of-methods-for-the-detection-of-node-group-membership-in-bipartite-networks}
{Comparison of methods for the detection of node group membership in bipartite networks}
\newline
Sawardecker EN, Amundsen CA, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{European Physical Journal B}
    72:
671--677 (2009).
    [{\em{Citations:}}  6 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[79]}}
\href{/people/amaral/micro-bias-and-macro-performance}
{Micro-bias and macro-performance}
\newline
Seaver SMD, Moreira AA, Sales-Pardo M, Malmgren RD, Diermeier D, {\textbf{Amaral LAN}}
\newline
\textit{European Physical Journal B}
    67:
369--375 (2009).
    [{\em{Citations:}}  3 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[78]}}
\href{/people/amaral/a-poissonian-explanation-for-heavy-tails-in-e-mail-communication}
{A Poissonian explanation for heavy tails in e-mail communication}
\newline
Malmgren RD, Stouffer DB, Motter AE, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    105:
18153--18158 (2008).
    [{\em{Citations:}}  156 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[77]}}
\href{/people/amaral/effectiveness-journal-ranking-schemes-as-tool-for-locating-information}
{Effectiveness of journal ranking schemes as a tool for locating information}
\newline
Stringer MJ, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{PLoS ONE}
    3:
e1683 (2008).
    [{\em{Citations:}}  58 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[76]}}
\href{/people/amaral/cascading-failure-and-robustness-in-metabolic-networks}
{Cascading failure and robustness in metabolic networks}
\newline
Smart AG, {\textbf{Amaral LAN}}, Ottino JM
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    105:
13223--13228 (2008).
    [{\em{Citations:}}  35 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[75]}}
\href{/people/amaral/chemical-amplification-in-an-invaded-food-web-seasonality-and-ontogeny-in-a-high-biomass-low-diversity-ecosystem}
{Chemical amplification in an invaded food web: Seasonality and ontogeny in a high-biomass, low-diversity ecosystem}
\newline
Ng CA, Berg MB, Jude DJ, Janssen J, Charlebois PM, {\textbf{Amaral LAN}}, Gray KA
\newline
\textit{Environmental Toxicology and Chemistry}
    27:
2186--2195 (2008).
    [{\em{Citations:}}  14 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[74]}}
\href{/people/amaral/extracting-the-hierarchical-organization-of-complex-systems}
{Extracting the hierarchical organization of complex systems}
\newline
Sales-Pardo M, Guimer\`a R, Moreira AA, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    104:
15224--15229 (2007).
    [{\em{Citations:}}  221 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[73]}}
\href{/people/amaral/module-identification-in-bipartite-and-directed-networks}
{Module identification in bipartite and directed networks}
\newline
Guimer\`a R, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review E}
    76:
036102 (2007).
    [{\em{Citations:}}  155 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[72]}}
\href{/people/amaral/classes-of-complex-networks-defined-by-role-to-role-connectivity-profiles}
{Classes of complex networks defined by role-to-role connectivity profiles}
\newline
Guimer\`a R, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{Nature Physics}
    3:
63--69 (2007).
    [Highlighted in cover]
    [{\em{Citations:}}  150 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[71]}}
\href{/people/amaral/evidence-for-the-existence-of-a-robust-pattern-of-prey-selection-in-food-webs}
{Evidence for the existence of a robust pattern of prey selection in food webs}
\newline
Stouffer DB, Camacho J, Jiang W, {\textbf{Amaral LAN}}
\newline
\textit{Proc. R. Soc. B-Biol. Sci.}
    274:
1931--1940 (2007).
    [{\em{Citations:}}  68 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[70]}}
\href{/people/amaral/a-network-based-method-for-target-selection-in-metabolic-networks}
{A network-based method for target selection in metabolic networks}
\newline
Guimer\`a R, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{Bioinformatics}
    23:
1616--1622 (2007).
    [{\em{Citations:}}  35 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[69]}}
\href{/people/amaral/quantitative-analysis-of-the-local-structure-of-food-webs}
{Quantitative analysis of the local structure of food webs}
\newline
Camacho J, Stouffer DB, {\textbf{Amaral LAN}}
\newline
\textit{Journal of Theoretical Biology}
    246:
260--268 (2007).
    [{\em{Citations:}}  22 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[68]}}
\href{/people/amaral/evolution-of-protein-families-is-it-possible-to-distinguish-between-domains-of-life}
{Evolution of protein families: Is it possible to distinguish between domains of life?}
\newline
Sales-Pardo M, Chan AOB, {\textbf{Amaral LAN}}, Guimer\`a R
\newline
\textit{Gene}
    402:
81--93 (2007).
    [{\em{Citations:}}  2 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[67]}}
\href{/people/amaral/complex-fluctuations-and-robustness-in-stylized-signalling-networks}
{Complex fluctuations and robustness in stylized signalling networks}
\newline
Diaz-Guilera A, Moreira AA, Guzman L, {\textbf{Amaral LAN}}
\newline
\textit{Journal of Statistical Mechanics - Theory and Experiment}
P01013 (2007).
    [{\em{Citations:}}  1 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[66]}}
\href{/people/amaral/a-robust-measure-of-food-web-intervality}
{A robust measure of food web intervality}
\newline
Stouffer DB, Camacho J, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    103:
19015--19020 (2006).
    [{\em{Citations:}}  68 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[65]}}
\href{/people/amaral/functional-cartography-of-complex-metabolic-networks}
{Functional cartography of complex metabolic networks}
\newline
Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{Nature}
    433:
895--900 (2005).
    [{\em{Citations:}}  1172 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[64]}}
\href{/people/amaral/the-worldwide-air-transportation-network-anomalous-centrality-community-structure-and-cities-global-roles}
{The worldwide air transportation network: Anomalous centrality, community structure, and cities global roles}
\newline
Guimer\`a R, Mossa S, Turtschi A, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    102:
7794--7799 (2005).
    [Featured on cover]
    [{\em{Citations:}}  574 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[63]}}
\href{/people/amaral/team-assembly-mechanisms-determine-collaboration-network-structure-and-team-performance}
{Team assembly mechanisms determine collaboration network structure and team performance}
\newline
Guimer\`a R, Uzzi B, Spiro J, {\textbf{Amaral LAN}}
\newline
\textit{Science}
    308:
697--702 (2005).
    [{\em{Citations:}}  316 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[62]}}
\href{/people/amaral/cartography-of-complex-networks-modules-and-universal-roles}
{Cartography of complex networks: modules and universal roles}
\newline
Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{Journal of Statistical Mechanics - Theory and Experiment}
P02001 (2005).
    [{\em{Citations:}}  133 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[61]}}
\href{/people/amaral/mesoscopic-modeling-for-nucleic-acid-chain-dynamics}
{Mesoscopic modeling for nucleic acid chain dynamics}
\newline
Sales-Pardo M, Guimer\`a R, Moreira AA, Widom J, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review E}
    71:
051902 (2005).
    [{\em{Citations:}}  103 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[60]}}
\href{/people/amaral/quantitative-patterns-in-the-structure-of-model-and-empirical-food-webs}
{Quantitative patterns in the structure of model and empirical food webs}
\newline
Stouffer DB, Camacho J, Guimer\`a R, Ng CA, {\textbf{Amaral LAN}}
\newline
\textit{Ecology}
    86:
1301--1311 (2005).
    [{\em{Citations:}}  99 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[59]}}
\href{/people/amaral/canalizing-kauffman-networks-nonergodicity-and-its-effect-on-their-critical-behavior}
{Canalizing Kauffman networks: Nonergodicity and its effect on their critical behavior}
\newline
Moreira AA, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    94:
218702 (2005).
    [{\em{Citations:}}  38 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[58]}}
\href{/people/amaral/scaling-phenomena-in-the-growth-dynamics-of-scientific-output}
{Scaling phenomena in the growth dynamics of scientific output}
\newline
Matia K, {\textbf{Amaral LAN}}, Luwel M, Moed HF, Stanley HE
\newline
\textit{Journal of the American Society for Information Science and Technology}
    56:
893--902 (2005).
    [{\em{Citations:}}  19 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[57]}}
\href{/people/amaral/modularity-from-fluctuations-in-random-graphs-and-complex-networks}
{Modularity from fluctuations in random graphs and complex networks}
\newline
Guimer\`a R, Sales-Pardo M, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review E}
    70:
025101 (2004).
    [{\em{Citations:}}  330 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[56]}}
\href{/people/amaral/modeling-the-world-wide-airport-network}
{Modeling the world-wide airport network}
\newline
Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{European Physical Journal B}
    38:
381--385 (2004).
    [{\em{Citations:}}  200 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[55]}}
\href{/people/amaral/emergence-of-complex-dynamics-in-a-simple-model-of-signaling-networks}
{Emergence of complex dynamics in a simple model of signaling networks}
\newline
{\textbf{Amaral LAN}}, Diaz-Guilera A, Moreira AA, Goldberger AL, Lipsitz LA
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    101:
15551--15555 (2004).
    [Highlighted in cover]
    [{\em{Citations:}}  66 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[54]}}
\href{/people/amaral/efficient-system-wide-coordination-in-noisy-environments}
{Efficient system-wide coordination in noisy environments}
\newline
Moreira AA, Mathur A, Diermeier D, {\textbf{Amaral LAN}}
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    101:
12085--12090 (2004).
    [{\em{Citations:}}  38 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[53]}}
\href{/people/amaral/heuristic-segmentation-of-a-nonstationary-time-series}
{Heuristic segmentation of a nonstationary time series}
\newline
Fukuda K, Stanley HE, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review E}
    69:
021108 (2004).
    [{\em{Citations:}}  30 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[52]}}
\href{/people/amaral/decreased-fractal-correlation-in-diurnal-physical-activity-in-chronic-fatigue-syndrome}
{Decreased fractal correlation in diurnal physical activity in chronic fatigue syndrome}
\newline
Ohashi K, Bleijenberg G, van der Werf S, Prins J, {\textbf{Amaral LAN}}, Natelson BH, Yamamoto Y
\newline
\textit{Methods of Information in Medicine }
    43:
26--29 (2004).
    [{\em{Citations:}}  13 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[51]}}
\href{/people/amaral/power-law-temporal-auto-correlations-in-day-long-records-of-human-physical-activity-and-their-alteration-with-disease}
{Power law temporal auto-correlations in day-long records of human physical activity and their alteration with disease}
\newline
{\textbf{Amaral LAN}}, Soares DJB, da Silva LR, Lucena LS, Saito M, Kumano H, Aoyagi N, Yamamoto Y
\newline
\textit{Europhysics Letters}
    66:
448--454 (2004).
    [{\em{Citations:}}  7 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[50]}}
\href{/people/amaral/asymmetrical-singularities-in-real-world-signals}
{Asymmetrical singularities in real-world signals}
\newline
Ohashi K, {\textbf{Amaral LAN}}, Natelson BH, Yamamoto Y
\newline
\textit{Physical Review E}
    68:
065204 (2003).
    [{\em{Citations:}}  33 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[49]}}
\href{/people/amaral/similarities-between-communication-dynamics-in-the-internet-and-the-autonomic-nervous-system}
{Similarities between communication dynamics in the Internet and the autonomic nervous system}
\newline
Fukuda K, {\textbf{Amaral LAN}}, Stanley HE
\newline
\textit{Europhysics Letters}
    62:
189--195 (2003).
    [{\em{Citations:}}  24 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[48]}}
\href{/people/amaral/sexual-contacts-and-epidemic-thresholds-reply}
{Sexual contacts and epidemic thresholds - Reply}
\newline
Liljeros F, Edling CR, Stanley HE, Aberg Y, {\textbf{Amaral LAN}}
\newline
\textit{Nature}
    423:
606 (2003).
    [{\em{Citations:}}  8 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[47]}}
\href{/people/amaral/dynamics-of-temporal-correlation-in-daily-internet-traffic}
{Dynamics of temporal correlation in daily Internet traffic}
\newline
Fukuda K, {\textbf{Amaral LAN}}, Stanley HE
\newline
\textit{IEEE 2003 Global Communications Conference (GlobeComm 2003)}
4069--4073 (2003).
    [{\em{Citations:}}  4 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[46]}}
\href{/people/amaral/random-matrix-approach-to-cross-correlations-in-financial-data}
{Random matrix approach to cross correlations in financial data}
\newline
Plerou V, Gopikrishnan P, Rosenow B, {\textbf{Amaral LAN}}, Guhr T, Stanley HE
\newline
\textit{Physical Review E}
    65:
066126 (2002).
    [{\em{Citations:}}  344 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[45]}}
\href{/people/amaral/robust-patterns-in-food-web-structure}
{Robust patterns in food web structure}
\newline
Camacho J, Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    88:
228102 (2002).
    [{\em{Citations:}}  154 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[44]}}
\href{/people/amaral/truncation-of-power-law-behavior-in-scale-free-network-models-due-to-information-filtering}
{Truncation of power law behavior in scale-free network models due to information filtering}
\newline
Mossa S, Barthelemy M, Stanley HE, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    88:
138701 (2002).
    [{\em{Citations:}}  88 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[43]}}
\href{/people/amaral/dynamics-of-sleep-wake-transitions-during-sleep}
{Dynamics of sleep-wake transitions during sleep}
\newline
Lo CC, {\textbf{Amaral LAN}}, Havlin S, Ivanov PC, Penzel T, Peter JH, Stanley HE
\newline
\textit{Europhysics Letters}
    57:
625--631 (2002).
    [{\em{Citations:}}  56 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[42]}}
\href{/people/amaral/analytical-solution-of-a-model-for-complex-food-webs}
{Analytical solution of a model for complex food webs}
\newline
Camacho J, Guimer\`a R, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review E}
    65:
030901 (2002).
    [{\em{Citations:}}  51 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[41]}}
\href{/people/amaral/different-scaling-behaviors-of-commodity-spot-and-future-prices}
{Different scaling behaviors of commodity spot and future prices}
\newline
Matia K, {\textbf{Amaral LAN}}, Goodwin SP, Stanley HE
\newline
\textit{Physical Review E}
    66:
045103 (2002).
    [{\em{Citations:}}  36 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[40]}}
\href{/people/amaral/extremum-statistics-in-scale-free-network-models}
{Extremum statistics in scale-free network models}
\newline
Moreira AA, Andrade JS, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    89:
268703 (2002).
    [{\em{Citations:}}  26 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[39]}}
\href{/people/amaral/scaling-in-the-growth-of-geographically-subdivided-populations-invariant-patterns-from-a-continent-wide-biological-survey}
{Scaling in the growth of geographically subdivided populations: invariant patterns from a continent-wide biological survey}
\newline
Keitt TH, {\textbf{Amaral LAN}}, Buldyrev SV, Stanley HE
\newline
\textit{Philos. Trans. R. Soc. Lond. Ser. B-Biol. Sci.}
    357:
627--633 (2002).
    [{\em{Citations:}}  16 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[38]}}
\href{/people/amaral/the-web-of-human-sexual-contacts}
{The web of human sexual contacts}
\newline
Liljeros F, Edling CR, {\textbf{Amaral LAN}}, Stanley HE, Aberg Y
\newline
\textit{Nature}
    411:
907--908 (2001).
    [{\em{Citations:}}  938 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[37]}}
\href{/people/amaral/behavioral-independence-features-of-complex-heartbeat-dynamics}
{Behavioral-independent features of complex heartbeat dynamics}
\newline
{\textbf{Amaral LAN}}, Ivanov PC, Aoyagi N, Hidaka I, Tomono S, Goldberger AL, Stanley HE, Yamamoto Y
\newline
\textit{Physical Review Letters}
    86:
6026--6029 (2001).
    [{\em{Citations:}}  137 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[36]}}
\href{/people/amaral/scale-invariance-in-the-nonstationarity-of-human-heart-rate}
{Scale invariance in the nonstationarity of human heart rate}
\newline
Bernaola-Galvan P, Ivanov PC, {\textbf{Amaral LAN}}, Stanley HE
\newline
\textit{Physical Review Letters}
    87:
168105 (2001).
    [{\em{Citations:}}  87 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[35]}}
\href{/people/amaral/small-world-networks-and-the-conformation-space-of-a-short-lattice-polymer-chain}
{Small-world networks and the conformation space of a short lattice polymer chain}
\newline
Scala A, {\textbf{Amaral LAN}}, Barthelemy M
\newline
\textit{Europhysics Letters}
    55:
594--600 (2001).
    [{\em{Citations:}}  64 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[34]}}
\href{/people/amaral/application-of-statistical-physics-methods-and-concepts-to-the-study-of-science-technology-systems}
{Application of statistical physics methods and concepts to the study of science and technology systems}
\newline
{\textbf{Amaral LAN}}, Gopikrishnan P, Matia K, Plerou V, Stanley HE
\newline
\textit{Scientometrics}
    51:
9--36 (2001).
    [{\em{Citations:}}  13 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[33]}}
\href{/people/amaral/physiobank-physiotoolkit-and-physionet-components-of-a-new-research-resource-for-complex-physiologic-signals}
{PhysioBank, PhysioToolkit, and PhysioNet - Components of a new research resource for complex physiologic signals}
\newline
Goldberger AL, {\textbf{Amaral LAN}}, Glass L, Hausdorff JM, Ivanov PC, Mark RG, Mietus JE, Moody GB, Peng CK, Stanley HE
\newline
\textit{Circulation}
    101:
E215--E220 (2000).
    [{\em{Citations:}}  2182 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[32]}}
\href{/people/amaral/classes-of-small-world-networks}
{Classes of small-world networks}
\newline
{\textbf{Amaral LAN}}, Scala A, Barthelemy M, Stanley HE
\newline
\textit{Proc. Natl. Acad. Sci. U. S. A.}
    97:
11149--11152 (2000).
    [{\em{Citations:}}  1141 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[31]}}
\href{/people/amaral/economic-fluctuations-and-anomalous-diffusion}
{Economic fluctuations and anomalous diffusion}
\newline
Plerou V, Gopikrishnan P, {\textbf{Amaral LAN}}, Gabaix X, Stanley HE
\newline
\textit{Physical Review E}
    62:
R3023--R3026 (2000).
    [{\em{Citations:}}  141 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[30]}}
\href{/people/amaral/multifractality-in-human-heartbeat-dynamics}
{Multifractality in human heartbeat dynamics}
\newline
Ivanov PC, {\textbf{Amaral LAN}}, Goldberger AL, Havlin S, Rosenblum MG, Struzik ZR, Stanley HE
\newline
\textit{Nature}
    399:
461--465 (1999).
    [{\em{Citations:}}  790 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[29]}}
\href{/people/amaral/universal-and-nonuniversal-properties-of-cross-correlations-in-financial-time-series}
{Universal and nonuniversal properties of cross correlations in financial time series}
\newline
Plerou V, Gopikrishnan P, Rosenow B, {\textbf{Amaral LAN}}, Stanley HE
\newline
\textit{Physical Review Letters}
    83:
1471--1474 (1999).
    [{\em{Citations:}}  548 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[28]}}
\href{/people/amaral/scaling-of-the-distribution-of-fluctuations-of-financial-market-indices}
{Scaling of the distribution of fluctuations of financial market indices}
\newline
Gopikrishnan P, Plerou V, {\textbf{Amaral LAN}}, Meyer M, Stanley HE
\newline
\textit{Physical Review E}
    60:
5305--5316 (1999).
    [{\em{Citations:}}  489 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[27]}}
\href{/people/amaral/scaling-of-the-distribution-of-price-fluctuations-of-individual-companies}
{Scaling of the distribution of price fluctuations of individual companies}
\newline
Plerou V, Gopikrishnan P, {\textbf{Amaral LAN}}, Meyer M, Stanley HE
\newline
\textit{Physical Review E}
    60:
6519--6529 (1999).
    [{\em{Citations:}}  312 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[26]}}
\href{/people/amaral/small-world-networks-evidence-for-a-crossover-picture}
{Small-world networks: Evidence for a crossover picture}
\newline
Barthelemy M, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    82:
3180--3183 (1999).
    [{\em{Citations:}}  158 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[25]}}
\href{/people/amaral/sleep-wake-differences-in-scaling-behavior-of-the-human-heartbeat-analysis-of-terrestrial-and-long-term-space-flight-data}
{Sleep-wake differences in scaling behavior of the human heartbeat: Analysis of terrestrial and long-term space flight data}
\newline
Ivanov PC, Bunde A, {\textbf{Amaral LAN}}, Havlin S, Fritsch-Yelle J, Baevsky RM, Stanley HE, Goldberger AL
\newline
\textit{Europhysics Letters}
    48:
594--600 (1999).
    [{\em{Citations:}}  142 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[24]}}
\href{/people/amaral/similarities-between-the-growth-dynamics-of-university-research-and-of-competitive-economic-activities}
{Similarities between the growth dynamics of university research and of competitive economic activities}
\newline
Plerou V, {\textbf{Amaral LAN}}, Gopikrishnan P, Meyer M, Stanley HE
\newline
\textit{Nature}
    400:
433--437 (1999).
    [Highlighted in cover]
    [{\em{Citations:}}  83 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[23]}}
\href{/people/amaral/environmental-changes-coextinction-and-patterns-in-the-fossil-record}
{Environmental changes, coextinction, and patterns in the fossil record}
\newline
{\textbf{Amaral LAN}}, Meyer M
\newline
\textit{Physical Review Letters}
    82:
652--655 (1999).
    [{\em{Citations:}}  56 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[22]}}
\href{/people/amaral/small-world-networks-evidence-for-a-crossover-picture-vol-82-pg-3180-1999}
{Small-world networks: Evidence for a crossover picture (Erratum)}
\newline
Barthelemy M, {\textbf{Amaral LAN}}
\newline
\textit{Physical Review Letters}
    82:
5180--5180 (1999).
    [{\em{Citations:}}  38 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[21]}}
\href{/people/amaral/inverse-cubic-law-for-the-distribution-of-stock-price-variations}
{Inverse cubic law for the distribution of stock price variations}
\newline
Gopikrishnan P, Meyer M, {\textbf{Amaral LAN}}, Stanley HE
\newline
\textit{European Physical Journal B}
    3:
139--140 (1998).
    [{\em{Citations:}}  271 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[20]}}
\href{/people/amaral/power-law-scaling-for-a-system-of-interacting-units-with-complex-internal-structure}
{Power law scaling for a system of interacting units with complex internal structure}
\newline
{\textbf{Amaral LAN}}, Buldyrev SV, Havlin S, Salinger MA, Stanley HE
\newline
\textit{Physical Review Letters}
    80:
1385--1388 (1998).
    [{\em{Citations:}}  148 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[19]}}
\href{/people/amaral/universal-features-in-the-growth-dynamics-of-complex-organizations}
{Universal features in the growth dynamics of complex organizations}
\newline
Lee YK, {\textbf{Amaral LAN}}, Canning D, Meyer M, Stanley HE
\newline
\textit{Physical Review Letters}
    81:
3275--3278 (1998).
    [{\em{Citations:}}  131 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[18]}}
\href{/people/amaral/stochastic-feedback-and-the-regulation-of-biological-rhythms}
{Stochastic feedback and the regulation of biological rhythms}
\newline
Ivanov PC, {\textbf{Amaral LAN}}, Goldberger AL, Stanley HE
\newline
\textit{Europhysics Letters}
    43:
363--368 (1998).
    [{\em{Citations:}}  111 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[17]}}
\href{/people/amaral/scale-independent-measures-and-pathologic-cardiac-dynamics}
{Scale-independent measures and pathologic cardiac dynamics}
\newline
{\textbf{Amaral LAN}}, Goldberger AL, Ivanov PC, Stanley HE
\newline
\textit{Physical Reviews Letters}
    81:
2388--2391 (1998).
    [{\em{Citations:}}  100 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[16]}}
\href{/people/amaral/scaling-the-volatility-of-gdp-growth-rates}
{Scaling the volatility of GDP growth rates}
\newline
Canning D, {\textbf{Amaral LAN}}, Lee Y, Meyer M, Stanley HE
\newline
\textit{Economics Letters}
    60:
335--341 (1998).
    [{\em{Citations:}}  81 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[15]}}
\href{/people/amaral/comment-on-kinetic-roughening-in-slow-combustion-of-paper}
{Comment on Kinetic roughening in slow combustion of paper}
\newline
{\textbf{Amaral LAN}}, Makse HA
\newline
\textit{Physical Review Letters}
    80:
5706--5706 (1998).
    [{\em{Citations:}}  8 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[14]}}
\href{/people/amaral/scaling-behavior-in-economics-1-empirical-results-for-company-growth}
{Scaling behavior in economics: I Empirical results for company growth}
\newline
{\textbf{Amaral LAN}}, Buldyrev SV, Havlin S, Leschhorn H, Maass P, Salinger MA, Stanley HE, Stanley MHR
\newline
\textit{Journal de Physique I}
    7:
621--633 (1997).
    [{\em{Citations:}}  122 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[13]}}
\href{/people/amaral/scaling-behavior-in-economics-2-modeling-of-company-growth}
{Scaling behavior in economics: II. Modeling of company growth}
\newline
Buldyrev SV, {\textbf{Amaral LAN}}, Havlin S, Leschhorn H, Maass P, Salinger MA, Stanley HE, Stanley MHR
\newline
\textit{Journal de Physique I}
    7:
635--650 (1997).
    [{\em{Citations:}}  60 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[12]}}
\href{/people/amaral/universality-classes-for-rice-pile-models}
{Universality classes for rice-pile models}
\newline
{\textbf{Amaral LAN}}, Lauritsen KB
\newline
\textit{Physical Review E}
    56:
231--234 (1997).
    [{\em{Citations:}}  19 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[11]}}
\href{/people/amaral/impurity-induced-diffusion-bias-in-epitaxial-growth}
{Impurity-induced diffusion bias in epitaxial growth}
\newline
{\textbf{Amaral LAN}}, Krug J
\newline
\textit{Physical Review E}
    55:
7785--7788 (1997).
    [{\em{Citations:}}  10 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[10]}}
\href{/people/amaral/scaling-behaviour-in-the-growth-of-companies}
{Scaling behaviour in the growth of companies}
\newline
Stanley MHR, {\textbf{Amaral LAN}}, Buldyrev SV, Havlin S, Leschhorn H, Maass P, Salinger MA, Stanley HE
\newline
\textit{Nature}
    379:
804--806 (1996).
    [Featured on cover]
    [{\em{Citations:}}  363 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[9]}}
\href{/people/amaral/self-organized-critically-in-a-rice-pile-model}
{Self-organized criticality in a rice-pile model}
\newline
{\textbf{Amaral LAN}}, Lauritsen KB
\newline
\textit{Physical Review E}
    54:
R4512--R4515 (1996).
    [{\em{Citations:}}  34 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[8]}}
\href{/people/amaral/energy-avalanches-in-a-rice-pile-model}
{Energy avalanches in a rice-pile model}
\newline
{\textbf{Amaral LAN}}, Lauritsen KB
\newline
\textit{Physica A}
    231:
608--614 (1996).
    [{\em{Citations:}}  17 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[7]}}
\href{/people/amaral/scaling-properties-of-driven-interfaces-in-disordered-media}
{Scaling properties of driven interfaces in disordered media}
\newline
{\textbf{Amaral LAN}}, Barabasi AL, Makse HA, Stanley HE
\newline
\textit{Physical Review E}
    52:
4087--4104 (1995).
    [{\em{Citations:}}  69 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[6]}}
\href{/people/amaral/avalanches-and-the-directed-percolation-depinning-model-experiments-simulations-and-theory}
{Avalanches and the directed percolation depinning model - Experiments, simulations, and theory}
\newline
{\textbf{Amaral LAN}}, Barabasi AL, Buldyrev SV, Harrington ST, Havlin S, Sadr-Lahijany R, Stanley HE
\newline
\textit{Physical Review E}
    51:
4655--4673 (1995).
    [{\em{Citations:}}  45 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[5]}}
\href{/people/amaral/scaling-behavior-of-driven-interfaces-above-the-depinning-transition}
{Scaling behavior of driven interfaces above the depinning transition}
\newline
Makse HA, {\textbf{Amaral LAN}}
\newline
\textit{Europhysics Letters}
    31:
379--384 (1995).
    [{\em{Citations:}}  34 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[4]}}
\href{/people/amaral/dynamics-of-surface-roughening-with-quenched-disorder}
{Dynamics of surface roughening with quenched disorder}
\newline
Havlin S, {\textbf{Amaral LAN}}, Buldyrev SV, Harrington ST, Stanley HE
\newline
\textit{Physical Review Letters}
    74:
4205--4208 (1995).
    [{\em{Citations:}}  18 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[3]}}
\href{/people/amaral/universality-classes-for-interface-growth-with-quenched-disorder}
{Universality classes for interface growth with quenched disorder}
\newline
{\textbf{Amaral LAN}}, Barabasi AL, Stanley HE
\newline
\textit{Physical Review Letters}
    73:
62--65 (1994).
    [{\em{Citations:}}  84 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[2]}}
\href{/people/amaral/new-exponent-characterizing-the-effect-of-evaporation-on-imbibition-experiments}
{New exponent characterizing the effect of evaporation on imbibition experiments}
\newline
{\textbf{Amaral LAN}}, Barabasi AL, Buldyrev SV, Havlin S, Stanley HE
\newline
\textit{Physical Review Letters}
    72:
641--644 (1994).
    [{\em{Citations:}}  33 (Scopus) ]
\newline
\Gap
~
\Gap

\NumberedItem{\makebox[0.8cm][r]{[1]}}
\href{/people/amaral/monte-carlo-simulation-of-the-methylchloride-liquid-vapor-interface}
{Monte-Carlo simulation of the methylchloride liquid vapor interface}
\newline
{\textbf{Amaral LAN}}, Cabral BJC
\newline
\textit{Journal of Physics - Condensed Matter}
    5:
1919--1934 (1993).
    [{\em{Citations:}}  3 (Scopus) ]
\newline
\Gap
~
\Gap

\vspace*{0.2cm}\subsection
{Other Publications}
{Other Publications}
{PDF:Other_Publications}

\GapNoBreak
\NumberedItem{\makebox[0.8cm][r]{[1]}}
\href{/people/amaral/driving-on-cellular-pathway-66}
{Driving on cellular pathway \#66}
\newline
{\textbf{Amaral LAN}}
\newline
\textit{AIP Conf. Proc.}
    922:
641--646 (2007).
\newline
\Gap
~
\Gap

\vspace*{0.2cm}